Energy and the CES production function

### 2015-09-18 Articles/Article_EcolEcon_2015/EcolEcon_2015.Rnw
added another plot.

>>>>

<<>>=
ggplot(AllOE %>% mutate(split = interaction(Country, flavor, lex.order=TRUE))) +
  tri_theme() + 
  tri_grid() +
  tri_labels( labels = c("alpha[k]", "alpha[l]", "alpha[e]") ) +
  geom_tripath(alpha = 0.8, size = 1.2,
               aes(x = oe1, y = oe2, z = oe3,
                   alpha = Year, 
                   colour = flavor,
                   group = interaction(Country, nest, flavor)
               ) ) +
  facet_grid( nest~ Country)  +
  scale_colour_manual(values = c("black", "gray70")) 
@
